Maragra-CISM status report

### 2017-01-03 analyze_monthly_data.Rmd
monitoring or data entry

ggplot(data = x,
       aes(x = date,
           y = p)) +
  geom_bar(stat = 'identity') +
  xlab('Date') +
  ylab('Number of positive cases') +
    theme_wsj() +
  ggtitle('Malaria miscroscopy positive results',
          'All workers') +
  theme(title = element_text(size = 12))
```

>>>>

ggplot(data = x,
       aes(x = date,
           y = p)) +
  geom_bar(stat = 'identity') +
  xlab('Date') +
  ylab('Number of positive cases') +
    theme_fivethirtyeight() +
  ggtitle('Malaria miscroscopy positive results',
          'All workers') +
  theme(title = element_text(size = 12))
```
